\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-01-08 paper/supporting_information.tex
minor updates

We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible. Second, that the path traversed by the video trajectory should intersect itself as few times as possible.  The first criteria helps promote the ability to gain (albeit fuzzy) intuitions about similarities and differences between sections of video content based on their locations in the embedding space.  The second criteria was motivated by the low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions were consistent, but occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).  We formalized this optimization as the combination of values that satisfied
\[
\argmax_{\left\{K, \gamma, \delta, \tau, \varphi~\in~E~\mathrm{|}~\Phi\left(K, \gamma, \delta, \tau, \varphi \right) \right\}} \left[\mathrm{corr}\left(\Upsilon\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right),~\Upsilon\left(\chi\right)\right)\right],~\mathrm{where}
\]
\[
\Phi\left(K, \gamma, \delta, \tau, \varphi \right) = \argmin_{K, \gamma, \delta, \tau, \varphi} \left[\Gamma\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right)\right],
\]
$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersect.   The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.  The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, and $\varphi$ as a the sequences of average recall events, video events, and individuals' recall events, vertically concatenated.

>>>>

We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible. Second, that the path traversed by the embedded video trajectory should intersect itself a minimal number of times.  The first criteria helps bolster the validity of visual intuitions about relationships between sections of video content, based on their locations in the embedding space.  The second criteria was motivated by the observed low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions frequently occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).  We formalized this optimization as the combination of hyper-parameter values that satisfied
\[
\argmax_{\left\{K, \gamma, \delta, \tau, \varphi~\in~E~\mathrm{|}~\Phi\left(K, \gamma, \delta, \tau, \varphi \right) \right\}} \left[\mathrm{corr}\left(\Upsilon\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right),~\Upsilon\left(\chi\right)\right)\right],~\mathrm{where}
\]
\[
\Phi\left(K, \gamma, \delta, \tau, \varphi \right) = \argmin_{K, \gamma, \delta, \tau, \varphi} \left[\Gamma\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right)\right],
\]
$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.   The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.  The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, and $\varphi$ as a the sequences of average recall events, video events, and individuals' recall events, vertically concatenated.
